intro

### 2021-11-11 06_Paper/ER-ED/intro.Rmd
added text on ER process model

Every day we are confronted with stressful or emotionally demanding situations. 
The ability to modify emotional experiences, expressions and physiology [@Gross1998antecedent] regulate emotions is an important cognitive skill. 
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].

>>>>

Every day we are confronted with stressful or emotionally demanding situations. 
The ability to modify emotional experiences, expressions and physiology [@Gross1998antecedent] regulate emotions is an important cognitive skill. 
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
Different strategies can be used to regulate emotions.
So called antecedent-focused strategies, i.e., situation selection, situation modification, attentional deployment, and cognitive change take effect early in the emotion generation process.
The strategy response modification, in contrast, takes place late in the process and is therefore conceptualized as response-focused strategy [@Gross1998antecedent].
